Test a simpler version of veb-boost performance on ukbiobank data

### 2020-05-20 analysis/index.Rmd
test mr.ash2

## Test veb_boost
A simplified version: interative update of two mr.ash component

@@

  * [Using UKbiobank data (chr22)](simulation_simpleveb-boost_ukbchr22.html)

>>>>

## Test veb_boost
A simplified version: interative update of two mr.ash components

@@

  * [Using UKbiobank data (chr22)](simulation-simpleveb-boost-ukbchr22.html)

### 2020-05-20 analysis/simulation-simpleveb-boost-ukbchr22.Rmd
test mr.ash2

plot_pip <- function(indi, pip) {
  barplot(indi)
}

summary_mr.ash2 <- function(g.fit, s.fit, phenores){
  e.b <- rep(0, length(g.fit$beta))
  e.b[phenores$param$idx.cgene] <- phenores$param$e.beta
  cat("gene expression effect: \n")
  summary_mr.ash(g.fit)
  plot_beta(e.b, g.fit$beta)

>>>>

plot_pip <- function(indi, pip, pipcut = 0.1) {
  x <- barplot(indi, main = "PIP")
  points(x, pip, pch=19, col="red")
  pred <- which(pip > pipcut)
  real <- which(indi==1)
  tp <- length(intersect(pred, real))/length(pred)
  fp <- 1 - tp
  fn <- length(setdiff(real, pred))/length(real)
  cat("false positive rate: ", fp)
  cat("false negative rate: ", fn)
}

summary_mr.ash2 <- function(g.fit, s.fit, phenores, pipcut = 0.1){
  e.b <- rep(0, length(g.fit$beta))
  e.b[phenores$param$idx.cgene] <- phenores$param$e.beta
  cat("gene expression effect: \n")
  summary_mr.ash(g.fit)
  plot_beta(e.b, g.fit$beta)
  indi <- rep(0, length(g.fit$beta))
  indi[phenores$param$idx.cgene] <- 1
  pip <- get_pip(g.fit)
  plot_pip(indi, pip, pipcut = pipcut)
